Parallel Simulation of Adaptive Random Boolean Networks

### 2016-07-14 Paper/paper.tex
Cosmetics

	 Such representation supports different SpMV algorithms. These algorithms mainly aim at maximizing memory throughput and data locality, thus reducing the overall GPU kernel execution time. We chose compressed sparse-row (CSR) matrix storage format and implemented an SpMV kernel as described in \cite{bell2008efficient}, as it shows the best performance on unstructured matrices.

	However, the lenghts of attractors and transient periods grow faster than a power law[][] when the size of the network increases. This leads to a proportional growth of state updates one has to perform to find an attractor. The number of state updates turned out to be more important to the algorithm performance due to the lags between GPU kernel launches and the need to transfer data back from the GPU.

@@

	\begin{figure}[h]
		\begin{minipage}[t]{0.45\textwidth}
			\includegraphics[width=1.0\textwidth]{plots/evolution}
			\caption{Evolution of mean network connectivity}
			\label{fig:evolution}
		\end{minipage}\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=1.0\textwidth]{plots/attractors}
			\caption{Empirical distribution of attractor lengths}
			\label{fig:attractors}
		\end{minipage}
	\end{figure}
	%------------------------------------------------------------------------------
	\clearpage
	\section{Conclusion}
	The enormous size of RBN ensemble makes them appropriate to model various complex systems but also raises significant challenges for their numerical investigation. Even a problem of search for a single attractor of RBN is computationally hard for a networks larger than several dozens of nodes because of an exponential growth of a number of iterations with an increase of a network size.

>>>>

@@

	\begin{figure}[h]
		\begin{minipage}[t]{0.45\textwidth}
			\includegraphics[width=1.0\textwidth]{plots/evolution}
			\caption{Evolution of mean network connectivity}
			\label{fig:evolution}
		\end{minipage}\hfill
		\begin{minipage}[t]{0.45\textwidth}
			\centering
			\includegraphics[width=1.0\textwidth]{plots/attractors}
			\caption{Empirical distribution of attractor lengths}
			\label{fig:attractors}
		\end{minipage}
	\end{figure}
	%------------------------------------------------------------------------------
	\section{Conclusion}
	The enormous size of RBN ensemble makes them appropriate to model various complex systems but also raises significant challenges for their numerical investigation. Even a problem of search for a single attractor of RBN is computationally hard for a networks larger than several dozens of nodes because of an exponential growth of a number of iterations with an increase of a network size.
